03 Data Vizualization

### 2022-04-06 03_data_viz.Rmd
updated literature turnover plot

```{r lit search data}
lit_turnover_w_ours <- readxl::read_excel(file.path("data", "literature_turnover_rates.xlsx"))
```

@@

Generation time is related to the turnover rate as below:
$$
g = \frac{ln(2)}{\mu}
$$

@@

p_lit_turnover_w_ours <- lit_turnover_w_ours %>%
  # order by mean turnover rate
  ggplot(
    aes(x = n,
        y = u_d_mn,
        fill = method_type
        )
    ) +
  geom_col() +
  coord_flip() +
  scale_fill_manual(values = literature_values_swatch) +
  labs(y = TeX("Turnover (d$^{-1}$)")) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 0, hjust = 0.5),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "bottom",
        plot.title = element_text(hjust = 0.5))

# cowplot::save_plot(filename = "fig_output/p_lit_turnover_w_ours.pdf",
#                    plot = p_lit_turnover_w_ours,
#                    base_height = 8,
#                    base_width = 10)
```

@@

## Meta analysis of turnover rates in literature, grouped by method

>>>>

```{r lit search data}
lit_turnover <- readxl::read_excel(file.path("data", "literature_turnover_rates.xlsx"))
turnover_means <- turnover_weighted %>% 
  filter(inc_time_d == 7) %>%
  select(terrain, u_d_weighted) %>% 
  rename(u_d_mn = u_d_weighted) %>% 
  mutate(comment = terrain) %>% 
  mutate(n = case_when(
    terrain == "Niwot Ridge Tundra" ~ 3,
    terrain == "Gordon Gulch Conifer Forest" ~ 1,
    terrain == "Marshall Mesa Grassland" ~ 2
  )) %>% 
  mutate(method = "LH-SIP",
         method_type = "LH-SIP")

lit_turnover_w_ours <- lit_turnover %>% bind_rows(turnover_means)
```

@@

@@

p_lit_turnover_w_ours <- lit_turnover_w_ours %>%
  # order by mean turnover rate
  ggplot(
    aes(x = -n,
        y = u_d_mn,
        fill = method_type
        )
    ) +
  geom_col() +
  coord_flip(ylim = c(0, 0.5)) +
  scale_fill_manual(values = literature_values_swatch) +
  labs(y = TeX("Turnover (d$^{-1}$)"),
       fill = "Method") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 0, hjust = 0.5, size = 14),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 18),
        #legend.position = "bottom",
        plot.title = element_text(hjust = 0.5),
        legend.position = c(0.85, 0.1),
        legend.text = element_text(size = 15),
        legend.title = element_blank())
p_lit_turnover_w_ours

cowplot::save_plot(filename = "fig_output/literature_values.pdf",
                   plot = p_lit_turnover_w_ours,
                   base_height = 8,
                   base_width = 10)
```

@@
